A unified pseudo-$C_\ell$ framework

### 2018-08-06 doc/Paper/main.tex
debug toggle

\usepackage{lipsum}
\usepackage{lineno}
\linenumbers
\newcommand{\chg}[1]{{\textcolor{blue}{#1}}}
\newcommand{\as}[1]{{\textcolor{red}{[\textbf{AS}: #1]}}}
\newcommand{\dam}[1]{{\textcolor{green}{[\textbf{DA}: #1]}}}
\newcommand{\js}[1]
{{\textcolor{orange}
{[\textbf{JS}: #1]}}}
\newcommand{\todo}[1]{{\bf TODO: #1}}

@@

\begin{abstract}
  The pseudo-$C_\ell$ is an algorithm for estimation of the angular
  power and cross-power spectra that is very fast and in realistic
  cases also nearly optimal. The algorithm can be extended to deal
  with contaminant deprojection and $E/B$ purification, and can
  therefore be applied in a wide variety of scenarios of interest for
  current and future cosmological observations. This paper presents
  \nmt, a public, validated, robust, accurate and easy-to-use software
  package that, for the first time, provides a unified framework to
  compute angular cross-power spectra of any pair of spin-0 or spin-2
  fields, contaminated by an arbitrary number of linear systematics
  and requiring $B$- or $E$-mode purification, both in the sphere or
  in the flat-sky approximation. We describe the mathematical
  background of the estimator, including all the features above, and
  its software implementation in \nmt. We construct a validation suite
  that aims to resemble the types of observations that next-generation
  large-scale structure and ground-based CMB experiments will face,
  and use it to show that the code is able to recover the input power
  spectra in the most complex scenarios with no detectable
  bias. \nmt~can be found at \url{add_url}, and is provided with
  comprehensive documentation and a number of code examples to
  maximize its usefulness in the community.
\end{abstract}

@@

  \section{Code structure}\label{sec:structure}
    All of the methods described above have been implemented in a software package called \nmt\footnote{The code source is hosted in \url{add_url}, and its documentation can be found at \url{http://namaster.readthedocs.io/}.}. We briefly describe the code structure here.

@@

    \nmt~is open-source software and publicly available at \url{add_url}. To maximize the usefulness of this software for the community, it is accompanied by an extensive documentation and example code\footnote{See \url{add_url}.}. \nmt~is written in {\tt C} and {\tt OpenMP}-parallelized to maximize its performance, although we encourage its use through the companion {\tt python} wrapper, the fastest-growing language of choice in the analysis of astronomical data. The code is in constant development, and we will strive to implement further functionality to e.g. estimate covariance matrices, extend the range of supported sky pixelizations and enhance its computational performance.

>>>>

\usepackage{lipsum}
\usepackage{lineno}
\linenumbers

\usepackage{etoolbox}

\newtoggle{DEBUG}
\toggletrue{DEBUG}

\iftoggle{DEBUG}{
\newcommand{\chg}[1]{{\textcolor{blue}{#1}}}
\newcommand{\as}[1]{{\textcolor{red}{[\textbf{AS}: #1]}}}
\newcommand{\dam}[1]{{\textcolor{green}{[\textbf{DA}: #1]}}}
\newcommand{\js}[1]{{\textcolor{orange}{[\textbf{JS}: #1]}}}
\newcommand{\todo}[1]{{\bf TODO: #1}}
}{
\newcommand{\chg}[1]{}
\newcommand{\as}[1]{}
\newcommand{\dam}[1]{}
\newcommand{\js}[1]{}
\newcommand{\todo}[1]{}
}

@@

\begin{abstract}
  The pseudo-$C_\ell$ is an algorithm for estimation of the angular
  power and cross-power spectra that is very fast and in realistic
  cases also nearly optimal. The algorithm can be extended to deal
  with contaminant deprojection and $E/B$ purification, and can
  therefore be applied in a wide variety of scenarios of interest for
  current and future cosmological observations. This paper presents
  \nmt, a public, validated, robust, accurate and easy-to-use software
  package that, for the first time, provides a unified framework to
  compute angular cross-power spectra of any pair of spin-0 or spin-2
  fields, contaminated by an arbitrary number of linear systematics
  and requiring $B$- or $E$-mode purification, both in the sphere or
  in the flat-sky approximation. We describe the mathematical
  background of the estimator, including all the features above, and
  its software implementation in \nmt. We construct a validation suite
  that aims to resemble the types of observations that next-generation
  large-scale structure and ground-based CMB experiments will face,
  and use it to show that the code is able to recover the input power
  spectra in the most complex scenarios with no detectable
  bias. \nmt~can be found at \url{https://github.com/LSSTDESC/NaMaster}, and is provided with
  comprehensive documentation and a number of code examples to
  maximize its usefulness in the community.
\end{abstract}

@@

  \section{Code structure}\label{sec:structure}
    All of the methods described above have been implemented in a software package called \nmt\footnote{The code source is hosted in \url{https://github.com/LSSTDESC/NaMaster}, and its documentation can be found at \url{http://namaster.readthedocs.io/}.}. We briefly describe the code structure here.

@@

    \nmt~is open-source software and publicly available at \url{https://github.com/LSSTDESC/NaMaster}. To maximize the
    usefulness of this software for the community, it is accompanied
    by an extensive documentation and example code\footnote{See \url{
        https://github.com/LSSTDESC/NaMaster}.}. \nmt~is written in
    {\tt C} and {\tt OpenMP}-parallelized to maximize its performance,
    although we encourage its use through the companion {\tt python}
    wrapper, the fastest-growing language of choice in the analysis of
    astronomical data. The code is in constant development, and we
    will strive to implement further functionality to e.g. estimate
    covariance matrices, extend the range of supported sky
    pixelizations and enhance its computational performance.
